Optimizing the power of adaptive seamless designs using Bayesian Optimization

### 2020-07-24 main.tex

@@

Challenges
  \begin{itemize}
    \item Power is determined stochastically through simulation
    \item Number of treatments in stage 2 depends on \emph{selection strategy} ($k_2$): \\
    $n_{\text{treat}} = (k_1+1) \cdot n_{\text{stage1}} + (k_2+1) \cdot n_{\text{stage2}}$ \\
    Remember: $n_{\text{treat}}$, $k_1$ fixed.
    \begin{itemize}
      \item $k_2 = 1,2,3$ fixed if we \emph{select} 1/2/3 best arms.
      \item $k_2$ only as expected value through \underline{simulation} for \emph{epsilon} and \emph{threshold} strategy.
    \end{itemize}
    Optimize \emph{ratio} $r$ instead of $n_{\text{stage1}}$ and $n_{\text{stage2}}$.
    \begin{align}
      c &= \frac{n_{\text{treat}}}{(k_1 + 1) \cdot r + (k_2+1) \cdot (1-r)} \\
      \Rightarrow n_{\text{stage1}} &= r \cdot c \ \land\\
       n_{\text{stage2}} &= (1-r) \cdot c 
    \end{align}
    \item Problem: \underline{Simulation} depends on $n_{\text{stage1}}$ \\
      Solution: Adapt $n_{\text{stage1}}$ so that $\hat{n}_{\text{treat}}$ is close to given $n_{\text{treat}}$ and $r$.
  \end{itemize}

@@

\bibliographystyle{biometrical}
\bibliography{literature.bib}

>>>>

Assurance: \cite{stallard_optimal_2009}

@@

@@

\bibliographystyle{biometrical}
\bibliography{literature,literature_zotero}
